### 2021-09-11 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

(2) We have carefully considered and followed all the comments and suggestions related to the clarity of the writing, and made the new material a thoroughly revised manuscript.

(3) We have added 3 papers published in the IEEE Transactions on Circuits and Systems for Video Technology, which are most closely related to our manuscript, and analysed what is distinctive / new about our current manuscript related to these previously published papers.

\uline{
Research topics related to adversarial attacks includes digital watermarking \cite{9343885}, 3D face presentation attacks \cite{9303455} and adversarial defense \cite{9169672}.
Xiong et. al. \cite{9343885} generate digital watermarking by slightly modifying the pixel values of videos frame to protect video content from unauthorized access. Compared with \cite{9343885}, our purpose of modifying pixel values of video frames is attacking the tracker, instead of detecting the illegal distribution of a digital movie.
Jia et. al. \cite{9294085} generate 3D face artifacts to fool the face recognition system. Compared with \cite{9294085}, our method directly modifies the input of the network instead of changing the input of cameras using 3D face artifacts.
Wang et. al. \cite{9169672} propose white-box attack/defense methods for image classifiers. Compared with \cite{9169672}, we focus on attacking the object tracking networks instead of the image classification networks.
}

% 4 高晋1 2021 是一个相关滤波算法
\uline{Liu et. al. \cite{9376997} propose a correlation filtering tracking algorithm based on the visual memory multi-template update strategy.
% 5 高晋2 2021 是一个相关滤波算法
Liu et. al. \cite{9132673} construct a fuzzy aided detection module to boost the correlation filtering tracking system.}

@@

\textbf{Thanks for the good comment. For your convenience in cross-checking, the new text is given as follows.}

\uline{Before introducing the proposed method, we first revisit the popular adversarial example generation methods. One of the simplest methods to generate adversarial images $I^{adv}$ works by linearizing loss function in $L_{\infty}$ neighbourhood of a clean image and finds exact maximum of linearized function using following closed-form equation \cite{FGSM}:}
\begin{equation}
    I^{adv} = I + \epsilon \text{ sign} \bigl( \nabla_I L(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input image, and the values of the pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$. $L(I, y)$ is the cost function of the neural network for the attack purpose, given image $I$ and label $y$. $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size, and clipping pixel values of intermediate results after each step to ensure that they are in an $\epsilon$-neighbourhood of the original image.  This leads to the Basic Iterative Method (BIM) introduced in \cite{kurakin2017adversarial}:}
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = Clip_{I,\epsilon}\{I_N^{adv}+\alpha \text{ sign}(\nabla_I L(I_N^{adv},y_{true}))\},
    \end{gathered}
\end{equation}
\uline{where $Clip_{I, \epsilon} \left\{ I' \right\}$ is the function which performs per-pixel clipping of the image $I'$, so that the result will be in $L_{\infty}$ $\epsilon$-neighbourhood of the source image $I$.}

\textit{3. The descriptions of figures and tables are not self-explanatory.}

\textbf{Thanks for your advice and we have replaced the descriptions of figures and tables. The modification is shown as follows for the convience of cross checking.}

% table 2
\textbf{We have replaced ``Compared with baselines on perturbed GOT-Val dataset.'' with}
\uline{``Comparison of attack performance with 2 baseline methods on GOT-Val in terms of AO. Baseline1 performs untargeted attacks based on the UAP \cite{UAP} method. Baseline2 performs targeted attacks based on the adversarial patch \cite{patch} method.''}
\textbf{in Section of the revised manuscript.}

% table 6
\textbf{We have replaced ``Contribution of each loss on GOT-Val.'' with}
\uline{``Analysis of the impact of each loss component on GOT-Val.''}
\textbf{in Section of the revised manuscript.}

% table 7
\textbf{We have replaced ``Transferability to different backbones on GOT-Val.'' with}
\uline{``Transferability to different backbones on GOT-Val. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to two more different backbones of SiamFC++, i.e., ShuffleNet \cite{ShuffleNet} and AlexNet \cite{AlexNet}.''}
\textbf{in Section of the revised manuscript.}

% table 8
\textbf{We have replaced ``Transferability to different tracking architectures on OTB2015.'' with}
\uline{``Transferability to different tracking architectures on OTB2015. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to two more state-of-the-art anchor-based trackers: AlexNet-based SiamRPN \cite{SiamRPN} and ResNet-based SiamRPN++ \cite{SiamRPN++}.''}
\textbf{in Section of the revised manuscript.}

% table 10
\textbf{We have replaced ``Untargeted attack: Precision score on OTB2015.'' with}
\uline{``State-of-the-art comparison of untargeted attack performance on OTB2015 in terms of precision score.''}
\textbf{in Section of the revised manuscript.}

% table 11
\textbf{We have replaced ``Targeted attack: Precision score on OTB2015.'' with}
\uline{``State-of-the-art comparison of targeted attack performance on OTB2015 in terms of precision score.''}
\textbf{in Section of the revised manuscript.}

@@

\textit{4. I suggest adding the advantages \& limitations of the proposed method after experimental analysis and future works to the conclusion.}

\textbf{Thanks for the good commenet. As suggested, we have added the advantages \& limitations of the proposed method after experimental analysis and future works to the conclusion. For the convenience of your cross checking, the new added text is as follows:}

\uline{
Compared with other attack method, our method has two key advantages. First,
  % 通用的，也就是不需要进行网络推断或者梯度计算，因此使得可以在不消耗计算资源的同时执行攻击成为可能。
because our video-agnostic feature, we are fast, no need to network interferes or gradient calculation, making it possible to attack a real-world online-tracking system when we can not get access to the limited computational resources.
Second, the proposed perturbations show good transferability to other anchor free or anchor based trackers. 
  %(1) Physical attack. We are the digital attack, which means ... Physical attack is ... The advantage of it is ... Our work assumes a threat model in which the adversary can feed data directly into the machine learning classifier. This is not always the case for systems operating in the physical world, for example those which are using signals from cameras and other sensors as input.
  % 这不就是 ICCV2019 的工作吗？它们也通用？好像是。EOT是通用的吗？
The main limitation of our work is the perturbation values are not as small as ohter non-universal perturbations due to the task difficulty.
% Future work:
  % (1) We need to do the physical attack.
  % (2) We need to be imperceptible.
  % 使用同一个扰动同时攻击多个视觉任务，包括图像分类，检测，视频目标跟踪和分割。
  In future work, we expect that it will be possible to demonstrate the existence of a single perturbation to attack multi vision tasks, including image classification, object detection and video object tracking/segementation.
  % 以更小的扰动取得更高的攻击效果。（呼应缺点之：扰动大）
  % Use more imperceptible perturbations to achieve high attack performance.
  % 本文所提出的对抗性信息被添加在数字图像上，从而影响跟踪器的跟踪效果。然而所提出的对抗性信息难以用于执行孪生跟踪器的物理攻击，即将对抗扰动打印出来添加到物理世界的真实目标上，从而影响孪生跟踪系统的性能。因为对抗扰动的打印过程可能改变扰动的值，且相机传感器可能无法感知较小的扰动。可能的解决方案是借助EOT生成针对相机距离和角度具有鲁棒性的物理扰动，使得在各种成像条件下，跟踪系统都无法对带有对抗性信息的真实目标进行正确跟踪。
  % 通过 *** 方式（比如，借助 *** 信息）实现物理攻击。
  % 防御？
}

@@

\textit{5. Some of the experiments require more explanations. For example, transferability has been investigated by different backbones \& architectures. It's needed to mention these experiments are with/without the training phase or not.}

\textbf{Thanks for point out this. These experiments do not need the training phase and we have added text to clarify this. For your convenience of cross checking, the new added text is as follows:}

\uline{These experiments do not need the training phase.}

@@

\textit{6. In experiments, I suggest considering two scenarios of different directions and trajectories.}

\textbf{We generate new trajectory without the test GT: we let the fake box run straight to border of the image, speed and derection is random.}

\uline{
Let us now turn to targeted attacks. In this context, we consider two scenarios:}
\begin{itemize}
  \item[] \uline{1. The attacker forces the tracker to follow a fixed direction. We illustrate this with 4 different directions, consisting of shifting the box by (3, 3) pixels in each consecutive frames, corresponding to the four directions 45, -45, 135, -135.}
  \item[] \uline{2. The attacker seeks for the tracker to follow a more complicated trajectory. ...}
\end{itemize}

### 2021-09-11 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

Thank you very much for your thorough review. Your insightful comments are very helpful for us to improve the quality of the paper. According to your comments and suggestions, we have carefully and extensively revised the manuscript. The main revised parts are highlighted by underlines in the underlined version for your convenience. You will find that all your comments and suggestions are considered and followed. We hope that our revised manuscript is now appropriate for publication in IEEE Transactions on Circuits and Systems for Video Technology.
In addition, point-to-point responses to your comments are given below and highlighted using bold font in line with your comments in order to facilitate cross-referencing.\\[10pt]
\indent We are looking forward to your reply.\\[10pt]
\noindent Yours sincerely,\\
\noindent Zhenbang Li, Yaya Shi, Jin Gao, Shaoru Wang, Bing Li, Pengpeng Liang, Weiming Hu
\\
\\
\\
\noindent Dr. Jin Gao (Contact author)\\
\noindent National Laboratory of Pattern Recognition (NLPR)\\
\noindent Institute of Automation, Chinese Academy of Sciences (CASIA)\\
\noindent Address: No. 95, Zhongguancun East Road, Haidian District,\\
\noindent Beijing 100190, P. R. China\\
\noindent Email: jin.gao@nlpr.ia.ac.cn

\newpage

%%%% 问题 3.1 %%%%
\textit{This paper employs the universal perturbation attacks on Siamese visual trackers. There are still the following concerns about the proposed method. 1. As stated in the paper, the proposed method ``does not require gradient optimization or network inference". However, this is a double-edged sword since it resulted in suspicious attacks. Prior works commonly train a network to prevent not only suspicious attacks but also modifying every pixel. I think it's a major problem with this work. I suggest considering a proper strategy to remove/reduce it.}

\textbf{
Thanks for your advice.
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在64*64这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of 64*64, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while having a targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of 64*64 in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are least sensitive that the Y channel. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The experimental result is shown in Table. As we can see, ...
For your convenience in cross-checking, the new text is given as follows.}

@@

\begin{figure}[t]
  \centering
  \subfigure[SSIM=0.85]{\label{fig:a}\includegraphics[width=0.15\textwidth]{images_imperceptible/2_adv_search_img_fgt.jpg}}
  \subfigure[SSIM=0.56]{\label{fig:a1}\includegraphics[width=0.15\textwidth]{images_imperceptible/64.jpg}}
  \subfigure[SSIM=0.79]{\label{fig:b}\includegraphics[width=0.15\textwidth]{images_imperceptible/16384_adv_template_img.jpg}}
  \subfigure[SSIM=0.79]{\label{fig:b}\includegraphics[width=0.15\textwidth]{images_imperceptible/template.jpg}}
  \caption{YCbCr Attack.}
  \label{fig:patch_size_vis}
\end{figure}

\uline{
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在64*64这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of 64*64, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while having a targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of 64*64 in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are least sensitive that the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The experimental result is shown in Table. As we can see, ...
% 分析攻击性能
The AO
% 分析可感知性
As shown in Figure, our new method can increase SSIM of the search image from 0.56 to 0.78. The template SSIM not change 0.79.
}

% \begin{table}[]
%   \begin{tabular}{lllllll}
%   \caption{Performance of the new attack method. We can see SSIM increases.}
%           & \multicolumn{2}{l}{Untargeted Attack} & \multicolumn{2}{l}{Targeted Attack} & \multirow{2}{*}{SSIM x} & \multirow{2}{*}{SSIM z} \\
%           & AO                & SR                & AO               & SR               &                         &                         \\
%   method1 & 0.1747            & 0.1442            & 0.8448           & 0.8972           & 0.56                    & 0.79                    \\
%   method2 &                   &                   &                  &                  & 0.78                    & 0.79                   
%   \end{tabular}
% \end{table}

@@

\textbf{We have replaced ``We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{LaSOT}, UAV123 \cite{UAV123}, VOT1016 \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}.'' with}
``\uline{We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k}, LaSOT \cite{LaSOT}, UAV123 \cite{UAV123}, VOT2016 \cite{VOT2016}, VOT2018 \cite{VOT2018} and VOT2019 \cite{VOT2019}.}''
\textbf{in Section IV.A of the revised manuscript.}

\textbf{We have replaced ``We adopt COCO \cite{COCO}, ILSVRC-VID \cite{VID} and the training splits of GOT-10k \cite{GOT-10k} and LaSOT \cite{LaSOT} as our training set. (see Table \ref{tab:dataset})'' with}
``\uline{We adopt COCO \cite{COCO}, ILSVRC-VID \cite{VID} and the training splits of GOT-10k \cite{GOT-10k} and LaSOT \cite{LaSOT} as our training set.}''
\textbf{in Section IV.B of the revised manuscript.}

\textit{8. Missing key ref : "Deep Learning for Visual Tracking: A Comprehensive Survey," in IEEE Transactions on Intelligent Transportation Systems, 2021.}

\textbf{Thanks for the good comment. We have cited this paper at Section II of the revised manuscript.  For your convenience in cross-checking, the new text is given as follows.}

### 2021-09-14 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

(3) We have added 3 papers published in the IEEE Transactions on Circuits and Systems for Video Technology, which are most closely related to our manuscript, and analysed what is distinctive / new about our current manuscript related to these previously published papers.

\uline{
Research topics related to adversarial attacks includes digital watermarking \cite{9343885}, 3D face presentation attacks \cite{9303455} and adversarial defense \cite{9169672}.
Xiong et. al. \cite{9343885} generate digital watermarking by slightly modifying the pixel values of videos frame to protect video content from unauthorized access. Compared with \cite{9343885}, our purpose of modifying pixel values of video frames is attacking the tracker, instead of detecting the illegal distribution of a digital movie.
Jia et. al. \cite{9294085} generate 3D face artifacts to fool the face recognition system. Compared with \cite{9294085}, our method directly modifies the input of the network instead of changing the input of cameras using 3D face artifacts.
Wang et. al. \cite{9169672} propose white-box attack/defense methods for image classifiers. Compared with \cite{9169672}, we focus on attacking the object tracking networks instead of the image classification networks.
}

% 4 高晋1 2021 是一个相关滤波算法
\uline{Liu et. al. \cite{9376997} propose a correlation filtering tracking algorithm based on the visual memory multi-template update strategy.
% 5 高晋2 2021 是一个相关滤波算法
Liu et. al. \cite{9132673} construct a fuzzy aided detection module to boost the correlation filtering tracking system.}

% 6 综述 2021
\uline{A comprehensive survey of the related trackers is beyond the scope of this paper, so we only briefly review trackers that are most relevant to our work: correlation-filtering based trackers and Siamese trackers. Please refer to \cite{9339950} for a thorough survey on visual object tracking methods.}

@@

\newgeometry{left=1cm,right=1cm,top=1cm,bottom=1cm}

\begin{figure*}[t!]
  \renewcommand\thefigure{9}
  \begin{center}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_BC.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_DEF.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_FM.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_IPR.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_IV.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_LR.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_MB.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_OCC.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_OPR.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_OV.png}
    \includegraphics[width=0.32\textwidth]{images_imperceptible/OTB2015/success_plot_OPE_OTB100_SV.png}
  \end{center}
      \caption{Untargeted attack results of the different trackers under the 11 attributes: out-of-view (OV), occlusion (OCC), illumination variation (IV), out-of-plane rotation (OPR), scale variation (SV),deformation (DEF), low resolution (LR), fast motion (FM), background clutters (BC), motion blur (MB), and in-plane rotation (IPR). The results show good transferability of our attacks to different tracking architectures, even if the generated perturbations are applied to anchor-based trackers.}
  \label{fig:attr}
\end{figure*}

\restoregeometry

%%%% 问题 1.4 %%%%
\textit{Also, some recent papers are valued to be referred (2020-2021), to enhance the quality.}

\textbf{Thanks for the good comments. We have added several 2020-2021 related papers to enhance the quality of the revised manuscript. For your convenience of cross review, the new text is given as follows.}

\uline{Research topics related to adversarial attacks includes digital watermarking \cite{9343885}, 3D face presentation attacks \cite{9303455} and adversarial defense \cite{9169672}.
Xiong et. al. \cite{9343885} generate digital watermarking by slightly modifying the pixel values of videos frame to protect video content from unauthorized access. Compared with \cite{9343885}, our purpose of modifying pixel values of video frames is attacking the tracker, instead of detecting the illegal distribution of a digital movie.
Jia et. al. \cite{9294085} generate 3D face artifacts to fool the face recognition system. Compared with \cite{9294085}, our method directly modifies the input of the network instead of changing the input of cameras using 3D face artifacts.
Wang et. al. \cite{9169672} propose white-box attack/defense methods for image classifiers. Compared with \cite{9169672}, we focus on attacking the object tracking networks instead of the image classification networks.}

@@

\textbf{For your convenience of cross checking, the new added text is shown as follows:}

\uline{
$A_{paste}$ means that, in the region where the perturbation is pasted, the pixel values of the original image is replaced with the pixel values of the perturbation.
% 解释加法
The operator $A_{add}$ means to apply additive noise, where the injecting small perturbations into the input samples. Often need constraint. the injected noise are small and sometimes invisible.  
}

%%%% 问题 2.2 %%%%
\textit{2. I agree with reviewer 3, the ground truth boxes are inaccessible to trackers during the inference. It seems that the authors use the ground truth boxes to generate the fake trajectory in lines 51-57 on page 7. Please clarify it.}

\uline
{
  \textit
  {
    Ablation Study: An alternative way to generate the fake trajectory
  }
  Here, we consider an alternative way to generate the \textit{fake trajectory}. Specifically, the attacker forces the tracker to follow a fixed direction. We illustrate this with 4 different directions, consisting of shifting the box by $(\pm 3, \pm 3)$ pixels in each consecutive frames, corresponding to the four directions $45^{\circ}, -45^{\circ}, 135^{\circ}, -135^{\circ}$.
}

\begin{table}[t]
  \centering
  \caption{Influence of different ways to generate the fake trajectory. One way is the fake trajectory to follow a fixed direction. The other way is the fake trajectory to follow the real target. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Type of the Fake Trajectory} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                              & AO                & SR                & AO               & SR               \\ \midrule
  Fixed direction             & 0.175             & 0.144             & 0.845            & 0.897            \\
  Follow the real target      & 0.153             & 0.123             & 0.840            & 0.890            \\ \bottomrule        
  \end{tabular}
  \label{table:direction}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{Influence of different ways to generate the fake trajectory. One way is the fake trajectory to follow a fixed direction. The other way is the fake trajectory to follow the real target. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{Type of the Fake Trajectory} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{2-5}
                              & AO                & SR                & AO               & SR               \\ \midrule
  Fixed direction             & 0.175             & 0.144             & 0.845            & 0.897            \\
  Follow the real target      & 0.153             & 0.123             & 0.840            & 0.890            \\ \bottomrule        
  \end{tabular}
  \label{table:direction}
\end{table}

%%%% 问题 2.3 %%%%
\textit{3. For the experiments, the authors should conduct the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$.}

\textbf{Thanks for your advice and we have conducted the ablation study on only adding perturbations on the template images or the search regions to show the impact of $p$ and $\delta$. As we can see, only use one of them is not useful, because they are trained together. For your convenience of cross review, the new text is given as follows.}

\uline{To see the impact of $p$ and $\delta$, we add the ablation study on only adding perturbations on the template images or the search regions. The result is shown in table \ref{table:one_branch}. Experiment results shows that only adding the perturbation to one branch is not useful.
% 对比无目标攻击性能。
For the untargeted attack, only attacking the template/search branch leads to the AO of 0.510/0.714, while attacking both branches leads to the AO of 0.153, which is more effective.
% 有目标
For the targeted attack, only attacking the templat/search branch leads to the AO of 0.156/0.160, while attacking both branches leads to the AO of 0.840. Experimental results show that attacking two branches can achieve better results than attacking one branch.}

\begin{table}[]
  \centering
  \caption{Attack performance when only use the template/search perturbation.}
  \label{table:one_branch}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
                & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\
                & AO                & SR                & AO               & SR               \\ \midrule
  Only Template & 0.510             & 0.567             & 0.156            & 0.106            \\
  Only Search   & 0.714             & 0.841             & 0.160            & 0.132            \\
  Both          & 0.153             & 0.123             & 0.840            & 0.890            \\
  \bottomrule
  \end{tabular}
\end{table}

@@

\textbf{
Thanks for your advice.
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在64*64这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of 64*64, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while having a targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of 64*64 in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are least sensitive that the Y channel. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The experimental result is shown in Table. As we can see, ...
For your convenience in cross-checking, the new text is given as follows.}

\begin{figure}[t]
  \centering
  \subfigure[SSIM=0.85]{\label{fig:a}\includegraphics[width=0.15\textwidth]{images_imperceptible/2_adv_search_img_fgt.jpg}}
  \subfigure[SSIM=0.56]{\label{fig:a1}\includegraphics[width=0.15\textwidth]{images_imperceptible/64.jpg}}
  \subfigure[SSIM=0.79]{\label{fig:b}\includegraphics[width=0.15\textwidth]{images_imperceptible/16384_adv_template_img.jpg}}
  \subfigure[SSIM=0.79]{\label{fig:b1}\includegraphics[width=0.15\textwidth]{images_imperceptible/template.jpg}}
  \caption{YCbCr Attack.}
  \label{fig:YCbCr}
\end{figure}

\begin{table}[t]
  \centering
  \caption{Influence of different ways to perturb the search image. One way is adding a small patch on the RGB channel. The other way is adding perturbation on the whole search image on the Y channel and add a small patch on the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:pertrub}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multirow{2}{*}[-2pt]{SSIM of x} & \multirow{2}{*}[-2pt]{SSIM of z} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{4-7}
                                                         &                                  &                                  & AO                & SR                & AO               & SR               \\ \midrule
  GRB Attack                                             & 0.56                             & 0.79                             & 0.246             & 0.227             & 0.682            & 0.756            \\
  YCbCr Attack                                           & 0.78                             & 0.79                             & 0.153             & 0.123             & 0.840            & 0.890            \\ \bottomrule        
  \end{tabular}
\end{table}

\uline{
% 承认已有问题：相比于现有的目标跟踪攻击算法，我们方法的不足之处是扰动值较为显眼。
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms.
% 解释我们的扰动显眼的原因：其他方法在整个搜索图像添加扰动，而我们必须要在64*64这个很小的区域内添加扰动，这增加了学习的难度，使得扰动值大。
Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of 64*64, which increases the learning difficulty and makes the perturbation values large.
% 解释我们不用全图攻击的原因：我们仅在小区域内而不是在整个搜索图像上添加扰动，因为必须指定轨迹在哪。
% 解决方案：为了既享受全图扰动带来的低感知性，以及局部扰动用于指定目标位置，我们考虑在不同的图像通道执行不同的扰动：首先将图像转为YCbCr通道，在Y通道做全图攻击，在CbCr通道做局部攻击。or: 为了在有目标攻击的同时降低可感知性，...
To reduce perceptibility while having a targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add pereturbations over the entire search image in the Y channel, and add perturbations over a very small region of 64*64 in the CbCr channel.
% 介绍什么是 YCbCr
Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection).
% 解释为什么用YCbCr而不是RGB。选择 YCbCr 而不是 RGB 的原因是更加独立。
We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}.
% 解释为什么在CbCr上做局部攻击在Y上做全图攻击，而不是其他方式：有研究证明Y通道可感知性更强而CbCr弱一些。因为我们希望补丁区域扰动值更小，所以我们在CbCr做局部攻击。
While considering the color sensitivity of human vision system, the CbCr channels are least sensitive that the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
% 实验细节：迭代了多少次？损失函数各项的权重是什么？模板图像怎么操作。
% 实验结果。
The experimental result is shown in Table \ref{table:pertrub}. As we can see,
% 分析攻击性能
the attack performance is slightly degraded. In terms of AO on GOT-VAL, the targeted attack performance changes from 0.840 to 0.680, and the untargeted attack performance changes from 0.153 to 0.246.
% 分析可感知性
As shown in Figure \ref{fig:YCbCr}, our new method can increase SSIM of the search image from 0.56 to 0.78. The template SSIM remains unchanged at 0.79.
}

@@

% \begin{table}[]
%   \begin{tabular}{lllllll}
%   \caption{Performance of the new attack method. We can see SSIM increases.}
%           & \multicolumn{2}{l}{Untargeted Attack} & \multicolumn{2}{l}{Targeted Attack} & \multirow{2}{*}{SSIM x} & \multirow{2}{*}{SSIM z} \\
%           & AO                & SR                & AO               & SR               &                         &                         \\
%   method1 & 0.1747            & 0.1442            & 0.8448           & 0.8972           & 0.56                    & 0.79                    \\
%   method2 &                   &                   &                  &                  & 0.78                    & 0.79                   
%   \end{tabular}
% \end{table}

%%%% 问题 3.2 %%%%
\textit{2. The proposed method and offline training phase should be explained more clearly. For instance, the termination of offline training or offline optimization is missed affecting perturbation values.}

\textbf{Thanks for the good comment. For your convenience in cross-checking, the new text is given as follows.}
